Paper_analyses

### 2021-07-27 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

split neutral positive and negative usign ground

@@

@@

@@

@@

@@

Pupil velocity test
# velocity analyses

>>>>

split neutral positive and negative using IAPS validation data and fit the same

@@

tmp.df4_full_stim_downs_jun2021_60bins$ground_arousal_lab
tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab

nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
# create and empty data-frame for the time-course analyses

View(timecourse_60bin_result_df_pos)
timecourse_60bin_result_df_pos <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       # Estimate_vl= rep(NA, 60), 
                                       # t_vl=rep(NA, 60), 
                                       # p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       # Estimate_ar_vl= rep(NA, 60), 
                                       # t_ar_vl=rep(NA, 60), 
                                       # p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

@@

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c + Mean_gray_z  +
                                (1 | ssid),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    ssid_num < 500 & ground_valence_lab == "More positive" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df_pos[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            #save the exact value of time bin
            # store arousal (2,parameter)            # first number is term(row), second is column
            timecourse_60bin_result_df_pos[i,2]<-
            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
            timecourse_60bin_result_df_pos[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_60bin_result_df_pos[i,4]<-
            lmer_bin_pup_summary[["coefficients"]][2,5] # p value

            timecourse_60bin_result_df_pos[i,5]<-
            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
            timecourse_60bin_result_df_pos[i,6]<-
              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
            timecourse_60bin_result_df_pos[i,7]<-
              lmer_bin_pup_summary[["coefficients"]][3,5] # p value

            timecourse_60bin_result_df_pos[i,8] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

@@

# timecourse_result_df_pos<- timecourse_result_df
View(timecourse_60bin_result_df_pos)

@@

# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05

timecourse_60bin_result_df_pos$p_ar_adj<- p.adjust(timecourse_60bin_result_df_pos$p_ar, method = "holm")
timecourse_60bin_result_df_pos$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_pos$p_ar_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_pos$p_br_adj <- p.adjust(timecourse_60bin_result_df_pos$p_br, method = "holm")
timecourse_60bin_result_df_pos$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_pos$p_br_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_pos[1:56,] %>%
  ggplot(aes(timebins, Estimate_ar))+
  geom_line(size = 1)+
  geom_line(aes(y = Estimate_br), linetype = "dashed", size = 1)

# subset(tmp.df4_full_stim_downs_jun2021_60bins,
#                                     ssid_num < 500 & ground_valence_lab == "More positive"
#                                    )%>%
#   # group_by(stimIAPS)%>%
#   # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
#   # ggplot(aes(valence, Mean))+
#   # geom_point()+
#   # geom_smooth(method = 'lm', se = F)+
#   # ggpubr::stat_cor()

```
neutral

nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
# create and empty data-frame for the time-course analyses

View(timecourse_60bin_result_df_pos)

timecourse_60bin_result_df_neutral <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       # Estimate_vl= rep(NA, 60), 
                                       # t_vl=rep(NA, 60), 
                                       # p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       # Estimate_ar_vl= rep(NA, 60), 
                                       # t_ar_vl=rep(NA, 60), 
                                       # p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c + Mean_gray_z  +
                                (1 | ssid),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    ssid_num < 500 & ground_valence_lab == "Mild" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df_neutral[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            #save the exact value of time bin
            # store arousal (2,parameter)            # first number is term(row), second is column
            timecourse_60bin_result_df_neutral[i,2]<-
            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
            timecourse_60bin_result_df_neutral[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_60bin_result_df_neutral[i,4]<-
            lmer_bin_pup_summary[["coefficients"]][2,5] # p value

            timecourse_60bin_result_df_neutral[i,5]<-
            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
            timecourse_60bin_result_df_neutral[i,6]<-
              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
            timecourse_60bin_result_df_neutral[i,7]<-
              lmer_bin_pup_summary[["coefficients"]][3,5] # p value

            timecourse_60bin_result_df_neutral[i,8] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

# timecourse_result_df_pos<- timecourse_result_df
View(timecourse_60bin_result_df_neutral)

timecourse_60bin_result_df_neutral$p_ar_adj<- p.adjust(timecourse_60bin_result_df_neutral$p_ar, method = "holm")
timecourse_60bin_result_df_neutral$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_neutral$p_ar_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_neutral$p_br_adj <- p.adjust(timecourse_60bin_result_df_neutral$p_br, method = "holm")
timecourse_60bin_result_df_neutral$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_neutral$p_br_adj<.05, TRUE, FALSE)

View(timecourse_60bin_result_df_neutral)
timecourse_60bin_result_df_neutral[1:56,] %>%
  ggplot(aes(timebins, Estimate_ar))+
  geom_line(size = 1)+
  geom_line(aes(y = Estimate_br), linetype = "dashed", size = 1)

@@

negative

nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
# create and empty data-frame for the time-course analyses

View(timecourse_60bin_result_df_pos)

timecourse_60bin_result_df_neg <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       # Estimate_vl= rep(NA, 60), 
                                       # t_vl=rep(NA, 60), 
                                       # p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       # Estimate_ar_vl= rep(NA, 60), 
                                       # t_ar_vl=rep(NA, 60), 
                                       # p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c + Mean_gray_z  +
                                (1 | ssid),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    ssid_num < 500 & ground_valence_lab == "More negative" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df_neg[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            #save the exact value of time bin
            # store arousal (2,parameter)            # first number is term(row), second is column
            timecourse_60bin_result_df_neg[i,2]<-
            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
            timecourse_60bin_result_df_neg[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_60bin_result_df_neg[i,4]<-
            lmer_bin_pup_summary[["coefficients"]][2,5] # p value

            timecourse_60bin_result_df_neg[i,5]<-
            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
            timecourse_60bin_result_df_neg[i,6]<-
              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
            timecourse_60bin_result_df_neg[i,7]<-
              lmer_bin_pup_summary[["coefficients"]][3,5] # p value

            timecourse_60bin_result_df_neg[i,8] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

# timecourse_result_df_pos<- timecourse_result_df
View(timecourse_60bin_result_df_neg)

# adjust p values
timecourse_60bin_result_df_neg$p_ar_adj<- p.adjust(timecourse_60bin_result_df_neg$p_ar, method = "holm")
timecourse_60bin_result_df_neg$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_neg$p_ar_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_neg$p_br_adj <- p.adjust(timecourse_60bin_result_df_neg$p_br, method = "holm")
timecourse_60bin_result_df_neg$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_neg$p_br_adj<.05, TRUE, FALSE)

View(timecourse_60bin_result_df_neg)

timecourse_60bin_result_df_neg[1:56,] %>%
  ggplot(aes(timebins, Estimate_ar))+
  geom_line(size = 1)+
  geom_line(aes(y = Estimate_br), linetype = "dashed", size = 1)

```
Pupil velocity test
# velocity analyses
